Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated ASE text

Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The modeling of a PV system is typically based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into Direct Current (DC) electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an Alternating Current (AC) load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\
%
Here the sizing check will be automatically performed by our proposed method; this stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 
%
Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
\begin{equation}
\label{eq:Ecorrected}
\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
%
\begin{equation}
\label{eq:Ep}
\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
\end{equation}

\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
%
The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
%
\begin{equation}
\label{eq:NTPmin}
\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
\end{equation}

Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
%
\begin{equation}
\label{eq:NPSmin}
\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
\end{equation}

\begin{equation}
\label{eq:NPPmin}
\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
\end{equation}

\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
%
Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
\begin{equation}
\label{eq:Cbank}
\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
\end{equation}
%
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
%
Secondly, the total (minimum) number of batteries is computed as 
\begin{equation}
\label{eq:Nbtotal}
\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
\end{equation}

Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
\scriptstyle V_{c} = \scriptstyle V_{system}.
\end{equation}

The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as 
%
\begin{equation}
\label{eq:iscamb}
\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
\end{equation}

The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
\begin{equation}
\label{eq:icmin}
\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
\end{equation}
%
\begin{equation}
\label{eq:icicmin}
\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
\end{equation}

The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\subsection{Optimal Sizing of PV Systems}
% -------------------------------------------------------
%
To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes our pseudocode to synthesize stand-alone PV systems using symbolic model checking. 
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}

 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requeriment enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requeriment enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requeriment enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

 \textcolor{red}{Could you please update the lines? I've reduced the number of lines of our algorithm above.}

Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5). After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8. The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 10 to 13). That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.

Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 14 to 20). The directive \textit{assume} (from Line 21 to 25) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements from Line 14 to 20 in addition to the Line 18. Therefore, our synthesis algorithm reaches Line 27 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$.

If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the items of each equipment and create a feasible solution. The main challenge for the {\sc Verify} phase is to find a feasible candidate solution regarding the constraints and user requirements, which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our {\sc Synthesize} phase. Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

\textbf{Case studies and setup.} We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. 
The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.

>>>>

Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into Direct Current (DC) electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an Alternating Current (AC) load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\
%
Here the sizing check will be automatically performed by our proposed method; this stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 
%
Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows
\begin{equation}
\label{eq:Ecorrected}
\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}
%
We also need to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, defined as
%
\begin{equation}
\label{eq:Ep}
\scriptstyle E_{p} = \scriptstyle Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
\end{equation}
%
\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.
%
The total minimum number of needed solar panels ($N_{TPmin}$) is computed as
%
\begin{equation}
\label{eq:NTPmin}
\scriptstyle N_{TPmin} = \dfrac{\scriptstyle E_{corrected}}{\scriptstyle E_{p}}.
\end{equation}
%
Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are respectively given by
%
\begin{equation}
\label{eq:NPSmin}
\dfrac{\scriptstyle V_{mppt,min}}{\scriptstyle V_{maxPower,TempMax}} \scriptstyle \leq \scriptstyle N_{PSmin} \leq \dfrac{\scriptstyle V_{mppt,max}}{\scriptstyle V_{maxPower,TempMin}},
\end{equation}
%
\begin{equation}
\label{eq:NPPmin}
\scriptstyle N_{PPmin} = \dfrac{\scriptstyle P_{total}}{\scriptstyle Number\,Panels\,Series \scriptstyle \times \scriptstyle P_{max,ref}},
\end{equation}
%
\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
%
Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
\begin{equation}
\label{eq:Cbank}
\scriptstyle C_{bank} \scriptstyle = \dfrac{\scriptstyle E_{corrected} \scriptstyle \times \scriptstyle autonomy}{\scriptstyle V_{system} \scriptstyle \times \scriptstyle DOD},
\end{equation}
%
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
%
Secondly, the total (minimum) number of batteries is computed as 
\begin{equation}
\label{eq:Nbtotal}
\scriptstyle N_{B}total = \scriptstyle N_{BS}min \scriptstyle \times \scriptstyle N_{BP}min = \dfrac{\scriptstyle V_{system}}{\scriptstyle V_{bat}} \scriptstyle \times \dfrac{\scriptstyle C_{bank}}{\scriptstyle 1 \,Battery \, Capacity}.
\end{equation}
%
Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
\scriptstyle V_{c} = \scriptstyle V_{system}.
\end{equation}
%
The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as 
%
\begin{equation}
\label{eq:iscamb}
\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
\end{equation}
%
The controller must meet the maximum current from the PV array given by Eqs. \eqref{eq:icmin} and \eqref{eq:icicmin} as
\begin{equation}
\label{eq:icmin}
\scriptstyle I_{c,min} = \scriptstyle I_{sc,amb} \times \scriptstyle N_{PP},
\end{equation}
%
\begin{equation}
\label{eq:icicmin}
\scriptstyle I_{c} \geq \scriptstyle I_{c,min}.
\end{equation}
%
The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\subsection{Optimal Sizing of PV Systems}
% -------------------------------------------------------
%
To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes our pseudocode to synthesize stand-alone PV systems using symbolic model checking. 
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requeriment enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requeriment enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requeriment enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
%
Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Line 2). After that, we define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5. The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (Lines 7 to 10). That procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combine them to assemble a feasible (candidate) PV solution, which meets the user requirements.

Next, we use Eq.~\eqref{eq:Ecorrected}, Eq.~\eqref{eq:Ep}, Eq.~\eqref{eq:NTPmin}, Eq.~\eqref{eq:NPSmin}, Eq.~\eqref{eq:NPPmin}, Eq.~\eqref{eq:Cbank}, Eq.~\eqref{eq:Nbtotal}, Eq.~\eqref{eq:iscamb}, and Eq.~\eqref{eq:icmin} to calculate the sizing variables (Lines 11 to 17). The directive \textit{assume} (Lines 15, 18 and 19) ensures the compatibility of the chosen items from the list of equipment: the {\sc Verify} phase uses only the item (among all the possible ones) that satisfies the statements of Lines 15, 18 and 19. Therefore, our synthesis algorithm reaches Line 20 with one feasible solution, and the cost of that solution is calculated in $F_{obj}$ (Line 21). 
If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the items of each equipment and create a feasible solution. The main challenge for the {\sc Verify} phase is to find a feasible candidate solution regarding the constraints and user requirements, which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our {\sc Synthesize} phase. Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
\textbf{Case studies and setup.} We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. 
The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.
